The Etiology of Cybersecurity

### 2022-04-24 reports/cimss_2022/main-cut.tex
Oliviero's feedback, pt. 2

\section{Introduction}\label{sec:intro}
\paragraph{Context and motivation.}
A \emph{scientific theory} is an explanation of a phenomenon such that the
explanation follows the scientific method. The \emph{scientific method} is an
\emph{empirical} method that aims at mitigating potential fallacies in
theories.  Karl Popper famously argued (e.g. in \autocite{Popper1959logic})
that a scientific theory can never be verified but only falsified, that a
theory should not be conceived by using the principle of
induction,\footnote{Einstein to Popper: ``[...] and I think (like
you, by the way) that theory cannot be fabricated out of the results of
observation, but that it can only be invented.'' \autocite{Popper1959logic}}
and that empirical experiments should be considered as the only evidence to
support the non-falseness of a scientific theory. 
In \autocite{Herley2016unfalsifiability}, Cormac Herley explores what he calls
``an asymmetry in computer security'', which he defines as follows: ``Things
can be declared insecure by observation, but not the reverse. There is no
observation that allows us to declare an arbitrary system or technique
secure''. With security, Herley only focuses on cybersecurity (we also use
security and insecurity, in this paper, only to refer to cyber-insecurity and
cybersecurity) and his intuition is that there is no scientific theory that can
predict the cybersecurity of a system, nor a theory that can predict all
possible insecurities of a system (which, by negation, may be used as a theory
of cybersecurity).  Herley then uses this argument to show that ``claims that
any measure is necessary for security are empirically unfalsifiable''.

>>>>

\section{Introduction}\label{sec:intro}
\paragraph{Context and motivation.}\ON{General: let us remind ourselves to address (at least discuss between us) the concerns of the reviewers.}
A \emph{scientific theory} is an explanation of a phenomenon such that the
explanation follows the scientific method. The \emph{scientific method} is an
\emph{empirical} method that aims at mitigating potential fallacies in
theories.  Karl Popper famously argued (e.g. in \autocite{Popper1959logic})
that a scientific theory can never be verified but only falsified, that a
theory should not be conceived by using the principle of
induction,\footnote{Einstein to Popper: ``[...] and I think (like
you, by the way) that theory cannot be fabricated out of the results of
observation, but that it can only be invented.'' \autocite{Popper1959logic}}
and that empirical experiments should be considered as the only evidence to
support the non-falseness of a scientific theory. 
In \autocite{Herley2016unfalsifiability}, Cormac Herley explores what he calls
``an asymmetry in computer security'', which he defines as follows: ``Things
can be declared insecure by observation, but not the reverse. There is no
observation that allows us to declare an arbitrary system or technique
secure''. With security, Herley only focuses on cybersecurity (we also use
security and insecurity, in this paper, only to refer to cyber-insecurity and
cybersecurity) and his intuition is that there is no scientific theory that can
predict the cybersecurity of a system, nor a theory that can predict all
possible insecurities of a system (which, by negation, may be used as a theory
of cybersecurity).  Herley then uses this argument to show that ``claims that
any measure is necessary for security are empirically unfalsifiable''.
